How to Analyze Build Logs---A~Comparative Study of Chunk~Retrieval~Techniques

### 2020-03-27 tse-paper/content.tex
More adaptations
Fix table

\begin{figure}[htb]
		\centering
		\includegraphics[width=\columnwidth, clip]{img/lit_survey.pdf}
		\caption{Our literature selection process, following \cite{petersen2015guidelines}.}
		\label{fig:lit-survey}
\end{figure}
\Cref{fig:lit-survey} presents an overview of our study selection.
In this first literature overview study on analyzing build logs, we
therefore want to survey as broad a population of scientific material
as possible. Note that we do not limit our sources to specific
Software Engineering venues, as is often done, but survey all sources
monitored by Google Scholar, including Bachelor's and Master's theses,
academic slide decks, and books. We use Google Scholar as opposed to
Scopus or other databases, as it is the search engine for acdemic
articles with the broadest and most current index, including preprints
from sources such as arXiv. One challenge is that no common
nomenclature has been established yet (in fact, this is one of the
goals of this article).

@@

\newpage
\subsection{Common Text Similarity (CTS)}

\begin{figure}[!t]
		\centering
		\includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-examplecount-CTS.pdf}
		\caption{Precision, recall and F$_{1}$-score of chunk retrieval with CTS for an increasing training set size.}
		\label{fig:recall-precision-examplecount-CTS}
\end{figure}

\begin{figure}[!t]
		\centering
		\includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-categorycount-CTS.pdf}
		\caption{Precision, recall and F$_{1}$-score of chunk retrieval with CTS for an increasing number of structural categories in the training and test sets.}
		\label{fig:recall-precision-categorycount-CTS}
\end{figure}

@@

\newpage
\subsection{Keyword Search (KWS)}

\begin{figure*}
\begin{subfigure}[b]{\columnwidth}
		\centering
		\includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-examplecount-KWS.pdf}
		\caption{Precision, recall and F$_{1}$-score for an increasing training set size.}
		\label{fig:recall-precision-examplecount-KWS}
\end{subfigure}\hspace{\fill}
\begin{subfigure}[b]{\columnwidth}
		\centering
		\includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-categorycount-KWS.pdf}
		\caption{Precision, recall and F$_{1}$-score for an increasing number of structural categories in the training and test sets.}
		\label{fig:recall-precision-categorycount-KWS}
\end{subfigure}
\caption{Results of chunk retrieval with  (KWS)}
\end{figure*}

@@

\newpage
\subsection{Program Synthesis by Example (PBE)}

\begin{figure*}
\begin{subfigure}[!t]{\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/recall-precision-examplecount-sythesisworked-PBE.pdf}
		\caption{Precision, recall and F$_{1}$-score when PBE could synthesize a consistent program compared with the size of the training set.}
		\label{fig:recall-precision-examplecount-sythesisworked-PBE}
\end{subfigure}

\begin{subfigure}[!t]{\textwidth}
		\centering
		\includegraphics[width=\textwidth, clip]{img/big-study/failure-reason-categorycount-PBE.pdf}
		\caption{Increasing number of structural categories in the training and test sets.}
		\label{fig:failure-reason-categorycount-PBE}
\end{subfigure}

\caption{Results of chunk retrieval with Program Synthesis by Example (PBE)}
\end{figure*}

@@

\subsection{Comparison of All Techniques}
\Cref{fig:success-partial-all} compares the success of chunk retrievals differentiated by techniques in our study.
CTS and KWS extract some of the desired lines in 79\% and 88.5\% of the chunk retrieval runs.
With 38.25\%, KWS also has the highest number of fully successful extractions, followed by PBE with 34.5\%.
PBE has the lowest number of partial retrievals with only 18 out of 400 chunk retrieval runs.

@@

\Cref{fig:recall-precision-singlecategory-all} and Figure~\ref{fig:recall-precision-multicategory-all} show the influence of a single structural category present in the training examples compared to multiple categories present.
For more than one present category, the recall of PBE decreases greatly.
For CTS and KWS the values also decrease, while RLR is not affected by the number of structural categories present.

@@

\begin{table}[tbp]
\centering
\begin{tabularx}{\columnwidth}{@{}llll@{}}
  \toprule
  & PBE & CTS & KWS \\
  \midrule
  Structural Categories & 1 & less is better & \makecell[l]{best 1 \\ multiple okay} \\
  Training Set Size & 2 & no influence & 2 \\ 
  Precision & \makecell[l]{high \\ (if synthesis succeeds)} & medium & low \\ 
  Recall & \makecell[l]{high \\ (if synthesis succeeds)} & medium & high \\ 
  \makecell[l]{Confidence in \\ Output Correctness} & high & low & \makecell[l]{low (precision) \\ high (recall)} \\ 
  Output Consumption by & program & human & human \\ 
  \bottomrule
\end{tabularx}
\caption{Recommendations for each of the investigated chunk retrieval techniques.}
\label{tab:single-technique-recommendations}
\end{table}

>>>>

\begin{figure}[htb]
        \centering
	\includegraphics[width=\columnwidth, clip]{img/lit_survey.pdf}
	\caption{Our literature selection process, following \cite{petersen2015guidelines}.}
	\label{fig:lit-survey}
\end{figure}

\Cref{fig:lit-survey} presents an overview of our study selection.
In this first literature overview study on analyzing build logs, we
therefore want to survey as broad a population of scientific material
as possible. Note that we do not limit our sources to specific
Software Engineering venues, as is often done, but survey all sources
monitored by Google Scholar, including Bachelor's and Master's theses,
academic slide decks, and books. We use Google Scholar as opposed to
Scopus or other databases, as it is the search engine for acdemic
articles with the broadest and most current index, including preprints
from sources such as arXiv. One challenge is that no common
nomenclature has been established yet (in fact, this is one of the
goals of this article).

@@

\newpage
\pagebreak
\subsection{Common Text Similarity (CTS)}

\begin{figure*}
\begin{subfigure}[t]{\columnwidth}
		\centering
                \includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-examplecount-CTS.pdf}
		\caption{Precision, recall and F$_{1}$-score of chunk retrieval with CTS for an increasing training set size.}
		\label{fig:recall-precision-examplecount-CTS}

\end{subfigure}\hspace{\fill}
\begin{subfigure}[t]{\columnwidth}
		\centering
                		\includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-categorycount-CTS.pdf}
		\caption{Precision, recall and F$_{1}$-score of chunk retrieval with CTS for an increasing number of structural categories in the training and test sets.}
		\label{fig:recall-precision-categorycount-CTS}
\end{subfigure}
\caption{Results of chunk retrieval with Common Text Similarity (CTS)}
\end{figure*}

@@

\newpage
\newpage
\subsection{Keyword Search (KWS)}

\begin{figure*}
\begin{subfigure}[b]{\columnwidth}
		\centering
		\includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-examplecount-KWS.pdf}
		\caption{Precision, recall and F$_{1}$-score for an increasing training set size.}
		\label{fig:recall-precision-examplecount-KWS}
\end{subfigure}\hspace{\fill}
\begin{subfigure}[b]{\columnwidth}
		\centering
		\includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-categorycount-KWS.pdf}
		\caption{Precision, recall and F$_{1}$-score for an increasing number of structural categories in the training and test sets.}
		\label{fig:recall-precision-categorycount-KWS}
\end{subfigure}
\caption{Results of chunk retrieval with Keyword Search (KWS)}
\end{figure*}

@@

\newpage
\newpage
\subsection{Program Synthesis by Example (PBE)}

\begin{figure*}
\begin{subfigure}[b]{\columnwidth}
		\centering
		\includegraphics[width=\columnwidth, clip]{img/big-study/recall-precision-examplecount-sythesisworked-PBE.pdf}
                		\caption{Precision, recall and F$_{1}$-score when PBE could synthesize a consistent program compared with the size of the training set.}
                \label{fig:recall-precision-examplecount-sythesisworked-PBE}
\end{subfigure}\hspace{\fill}
\begin{subfigure}[b]{\columnwidth}
		\centering
		\includegraphics[width=\columnwidth, clip]{img/big-study/failure-reason-categorycount-PBE.pdf}
                		\caption{Increasing number of structural categories in the training and test sets.}

                \label{fig:failure-reason-categorycount-PBE}
\end{subfigure}
\caption{Results of chunk retrieval with  Program Synthesis by Example (PBE)}
\end{figure*}

@@

\pagebreak
\subsection{Comparison of All Techniques}
\Cref{fig:success-partial-all} compares the success of chunk retrievals differentiated by techniques in our study.
CTS and KWS extract some of the desired lines in 79\% and 88.5\% of the chunk retrieval runs.
With 38.25\%, KWS also has the highest number of fully successful extractions, followed by PBE with 34.5\%.
PBE has the lowest number of partial retrievals with only 18 out of 400 chunk retrieval runs.

@@

\Cref{fig:recall-precision-singlecategory-all} and \Cref{fig:recall-precision-multicategory-all} show the influence of a single structural category present in the training examples compared to multiple categories present.
For more than one present category, the recall of PBE decreases greatly.
For CTS and KWS the values also decrease, while RLR is not affected by the number of structural categories present.

@@

\begin{table}[tbp]
\resizebox{\columnwidth}{!}{%
\centering
\begin{tabular}{llll}
  \toprule
  & PBE & CTS & KWS \\
  \midrule
  Structural Categories & 1 & less is better & \makecell[l]{best 1 \\ multiple okay} \\
  Training Set Size & 2 & no influence & 2 \\ 
  Precision & \makecell[l]{high \\ (if synthesis succeeds)} & medium & low \\ 
  Recall & \makecell[l]{high \\ (if synthesis succeeds)} & medium & high \\ 
  \makecell[l]{Confidence in \\ Output Correctness} & high & low & \makecell[l]{low (precision) \\ high (recall)} \\ 
  Output Consumption by & program & human & human \\ 
  \bottomrule
\end{tabular}%
}
\caption{Recommendations for each of the investigated chunk retrieval techniques.}
\label{tab:single-technique-recommendations}
\end{table}
